I gave 49 invited talks since 2022 at international universities, research institutes, and scholarly conferences and workshops, including 1 distinguished lecture, 2 keynotes, and 5 workshop keynotes. Additionally, I've given 18 invited talks within UCSB.

\smallskip
\noindent\textbf{Distinguished Lecture, Keynotes \& Workshop Keynotes}
\begingroup\small 
\begin{enumerate}[leftmargin=*,itemsep=0.1em,topsep=0.2em,parsep=0pt,partopsep=0pt]
    \item \textbf{Opening Keynote}, Geometric Science of Information (GSI), Saint-Malo. \textit{Topological Deep Learning} (2025).
    \item \textbf{Keynote}, NeurIPS Workshop on New Perspectives in Graph ML. \textit{Topological Deep Learning} (2025).
    \item \textbf{Keynote}, NeurIPS Workshop Mouse vs AI. \textit{The Algebra of Spatial Navigation} (2025).
    \item \textbf{Annual Tutte Lecture, Distinguished Speaker}, Ottawa. \textit{Geometric Computations in Natural and Artificial Brains} (2024).
    \item \textbf{Closing Keynote}, CZI Imaging The Future Annual Event. \textit{From Nano to Macro: Unlocking the Brain with AI-Driven Imaging Insights} (2024).
    \item \textbf{Keynote}, CVPR Workshop on Equivariance in Vision. \textit{Hierarchical Equivariance in Artificial and Natural Brains} (2024).
    \item \textbf{Keynote}, CVPR Workshop on Topology, Algebra and Geometry. \textit{Architectures of Topological Deep Learning} (2023).
    \item \textbf{Keynote}, CVPR Workshop on Deep Learning for Geometric Computing. \textit{Shape Learning in Biomedical Imaging} (2022).
\end{enumerate}
\endgroup




\smallskip
\noindent\textbf{Invited Talks at External Venues}
\begingroup\small 
\talksfile{sections/10_talkfiles/10_talks_external.tex}
\endgroup

\smallskip
\noindent\textbf{Invited Talks at UCSB}
\begingroup\small 
\talksfile{sections/10_talkfiles/10_talks_ucsb.tex}
\endgroup

