I co-founded the NeurReps workshop at NeurIPS (4 annual editions, 300--500 in-person attendees each year), organized 6 international workshops at top AI/ML venues, served as reviewer, grant panelist, member of scientific committees, and have served on multiple ECE department committees at UCSB.


\begingroup\small

\noindent\textbf{Conference \& Workshop Organization}
\begin{enumerate}[leftmargin=*,itemsep=0.1em,topsep=0.15em,parsep=0pt,partopsep=0pt]
    \item Co-founder and lead senior organizer, NeurIPS NeurReps Workshop on Symmetry and Geometry in Neural Representations (2022, 2023, 2024, 2025) --- \textbf{160+ accepted submissions and 300–500 in-person attendees each year}, and 20+ invited speakers across the four editions.
    \item Co-organizer, NeurIPS 2026 Workshop on Bridging Optimal Transport, Learning and Structured Data: Toward Geometric Distributional Learning. 
    \item Organizer, WIDS Datathon in partnership with Kaggle, Global \& University Editions (2025) --- \textbf{6,000+ participants from 99 countries.}
    \item Co-organizer, CVPR 2024 Workshop on Topological Deep Learning for Computer Vision.
    \item Lead co-organizer, BIRS 2023 Workshop on Mathematical Methods for Morphological Shapes across Biological Scales.
    \item Lead co-organizer, MICCAI 2022 Workshop on Topological Data Analysis and its Applications for Medical Data.
    \item Lead organizer, ICLR 2022 Workshop on Geometrical and Topological Representation Learning.
    \item Lead senior organizer of 6 AI/ML international challenges (2021-2026).
\end{enumerate}


\smallskip
\noindent\textbf{Peer Review \& Scientific Committees}
\begin{enumerate}[leftmargin=*,itemsep=0.1em,topsep=0.15em,parsep=0pt,partopsep=0pt]
    \item Reviewer for \textit{Nature}, \textit{Nature Communications}, \textit{NeurIPS}, \textit{ICML}, \textit{ICLR}, \textit{CVPR}, \textit{KDD}, \textit{JMLR}, \textit{Foundations of Computational Mathematics}, \textit{ACM Transactions on Mathematical Software}, \textit{Transactions on Graphics}, \textit{Journal of Mathematical Imaging and Vision}.
    \item Grant panel reviewer, NSF (Unsolicited Panel, 2022) and Keck Foundation (2026).
    \item Scientific Committee, Conference of Geometric Science of Information (GSI) --- 2017, 2019, 2021, 2023, 2025.
    \item Mentor, MIT Summer Geometry Institute (2021, 2022); London Geometry in Machine Learning Summer School (2022); Outreachy program for underrepresented populations (2021).
\end{enumerate}

\smallskip
\noindent\textbf{Department \& University Service}
\begin{enumerate}[leftmargin=*,itemsep=0.1em,topsep=0.15em,parsep=0pt,partopsep=0pt]
    \item Chair, ECE Public Relations Committee (2025--present).
    \item Member, ECE Grants Strategy Committee (2025--present).
    \item Member, ECE Seminars Committee (2022--2024).
    \item Member, ECE Graduate Admissions (2021--2023).
    \item Undergraduate Advisor, ECE (2021--2022).
\end{enumerate}

\smallskip
\noindent\textbf{Industry Advising \& Consulting}
\begin{enumerate}[leftmargin=*,itemsep=0.1em,topsep=0.15em,parsep=0pt,partopsep=0pt]
  \item Advisor, Atmo, Inc. (2021--present).
  \item Advisor and Consultant, New Theory, Inc. (2024--present).
  \item Consultant, Los Angeles Dodgers (2025).
  \item Consultant, CaranX (2022--2024).
\end{enumerate}
\endgroup