\noindent{\footnotesize\textbf{Bold}: candidate \quad \textbf{\textit{Italic Bold}}: advised Ph.D. student, visiting Ph.D. student, postdoc, or alumni}

\textbf{Op-Eds}
\begin{enumerate}[leftmargin=*,itemsep=0.2em,topsep=0.2em,parsep=0pt,partopsep=0pt]
    \item \textit{PLOS Biology}. ``Artificial Scientific Intelligence: The Fifth Era of Science.'' \textbf{Miolane} (2025).
    \item \textit{Inside Higher Ed}. ``Science Can't Depend on Corporate Goodwill.'' Lamar, \textbf{Miolane} (2025).
\end{enumerate}

\textbf{Press \& Podcasts}
\begin{enumerate}[leftmargin=*,itemsep=0.2em,topsep=0.2em,parsep=0pt,partopsep=0pt]
    \item \textit{Nature}. ``Brain differences between sexes get more pronounced from puberty.'' By Simms --- coverage of Huang, Jamison, Jacobs, \textbf{Miolane}, Kuceyeski (2026).
    \item \textit{The Transmitter}. ``Error equation predicts brain's ability to generalize.'' By Mesa --- featuring expert commentary by \textbf{Miolane} on neural geometry and AI (2026).
    \item \textit{The Economist} (podcast). ``We Don't Need No (AI) Education.'' \textit{\textbf{Bertics}}, Featuring \textbf{Miolane} (2025).
    \item \textit{The Transmitter}. ``How Neuroscientists Are Using AI.'' Featuring \textbf{Miolane} (2025).
    \item \textit{Science et Vie}. ``The Secrets of Our Thoughts Revealed by Mathematics.'' --- coverage of \textbf{Miolane}'s research (2023).
    \item \textit{TWiML} (podcast). ``Geometric Statistics in ML with Geomstats.'' --- \textbf{Miolane}'s interview (2018).
    \item \textit{France Inter} (podcast, national radio). ``Le Club de la Tête au Carré.'' Featuring \textbf{Miolane} (2016).
\end{enumerate}
