2024, November 14th. Keynote at the Chan-Zuckerberg Initiative Imaging The Future Annual Event. From Nano to Macro: Unlocking the Brain with AI-Driven Imaging Insights.

2024, November 9th. Outreach talk at the Lower East Side Girls Club. AI for Women’s Brain Health.

2024, October 15th. Talk at the Noyce Foundation Annual Event. The Role of AI in Advancing Women’s Brain Health.

2024, October. UCSB Board of Trustees. AI for Science.

2024, August 8th. Invited talk at The Battle of the Metrics Community Event at the Cognitive Computational Neuroscience (CCN2024). MIT, Boston. Riemannian Geometry of Neural Representations in Natural and Artificial Intelligence.

2024, July 27th. Keynote at the ICML GRaM Workshop (Geometry-grounded Representation Learning and Generative Modeling). Geometric Intelligence.

2024, July 15th. Keynote at the Eresfjord School of Mathematical Methods in Computational Neuroscience. Hierarchical Equivariance in Artificial and Natural Brains.

2024, June 18th. Keynote at the CVPR Equivision Workshop on Equivariance in Vision. Hierarchical Equivariance in Artificial and Natural Brains.

2024, June 17th. MIT DHIVE Program. Digital Twins and the Role of AI in Advancing Women’s Brain Health.

2024, May 28th. UC Riverside Seminar. Robust G-Invariance in G-Equivariant Networks.

2024, May 22nd. Distinguished Speaker for the Annual Tutte Lecture. Geometric Computations in Natural and Artificial Brains.

2024, May 13th. Ann S. Bowers Women’s Brain Health Seminar. Digital Twins and the Role of AI in Advancing Women’s Brain Health.

2024, February 15th. Lie Theory for Vision Grant Colloquium at UC Berkeley Redwood Center for Theoretical Neuroscience. Robust G-Invariance in G-Equivariant Networks.

2024, February 13th. Caltech’s Math \& Machine Learning Seminar. Robust G-Invariance in G-Equivariant Networks.

2024, February 9th. UCSB Physics Graduate Seminar. From theoretical physics to geometric intelligence.

2024, January 25th. Workshop of Graph Neural Networks for the Sciences. A survey of message passing topological neural networks.