2025, July 9th. Invited Talk at the Cold Spring Harbor Laboratory Seminar Series. Geometric Intelligence in Minds and Machines.

2025, June 18th. Invited Keynote at the UCSB Center for Aging and Longevity. Direct Relief, Santa Barbara. Healthy and Pathological Aging: Unlocking the Brain with AI.

2025, June 3rd. Invited Talk at the workshop “Bridging Biology and Statistics: Insights and Innovations for Modern Biology In Honor of Professor Susan Holmes”. Stanford University." The Role of AI in Advancing Women’s Brain Health.

2025, April 30th. Invited Talk at the workshop "New Developments in the Theory and Methodology of Graph Neural Networks", NSF-Simons National Institute for Mathematics and Theory in Biology (NITMB), Chicago. Topological Deep Learning.

2025, April 2nd. Invited Keynote at the Geometric Intelligence Workshop, Instituto de Matemáticas UNAM. Geometric Intelligence in Minds and Machines.

2025, March 31st. Invited Keynote at CoSyNe Workshop on GNNs and graphical analysis in neuroscience. A survey of message-passing topological neural networks.

2025, February 26th. Invited Keynote at the Center for Brain Health in Dallas. AI and the Digital Twin Brain.

2025, February 21st. Invited Keynote at the NeurReps Seminar Series. Geometric Intelligence in Minds and Machines.

2025, February 18th. Invited Talk at the Chan-Zuckerberg Initiative. Leveraging AI for Women’s Brain Health Research.

2025, February 10th. Invited Keynote at the Erwin Schrödinger International Institute. G-Invariance in G-Equivariant Networks.