2022, November 16th - UCSB ECE Graduate Seminar. Geometric Machine Learning.

2022, November 14th - UCLA ECE Seminar. Shape Learning in Biomedical Imaging.

2022, October 11th - INRIA Saclay, Seminar of the SODA / MIND (previously Parietal) teams. Geomstats: A Python Package for Geometry in Machine Learning.

2022, October 10th - Workshop Geometry, Topology in Statistics and Data Science of the Thematic Program of Institut Poincaré. Geomstats: A Python package for Geometry in Machine Learning.

2022, September 29th - SIAM Conference on Mathematics of Data Science. Mini Symposium of Statistics and Machine Learning in Topological and Geometric Data Analysis. Geomstats: A Python package for Differential Geometry in Machine Learning.

2022, September 7th - Geo2Int (Geometry and Geometric Integration) Workshop. Geomstats: A Python package for Differential Geometry in Machine Learning.

2022, June 20th - Keynote for the CVPR Deep Learning for Geometric Computing (DLGC) workshop. Shape Learning in Biomedical Imaging.

2022, June 8th - University of Washington, eScience Institute Semina and Geomstats Workshop. Geometric Learning for Shape Analysis in Bioimaging.

2022, June 1st - Sage Math conference. Geomstats: A Python package for Differential Geometry in Machine Learning.

2022, May 6th - Pacific Institute for the Mathematical Sciences (PIMS) workshop. CompSPI: Open-Source Software for Biological Imaging – Best Coding Practices.

2022, May 2nd - John Hopkins University Center for Imaging Science Workshop. Geometric Learning for Shape Analysis from Bioimaging. 

2022, April 13th - UCSB, Cryo-EM FIB Forum. Deep Generative Models for Molecular Reconstructions in Cryo-Electron Microscopy.

2022, March 11th - Psych \& Brain Sciences Department Seminar. Brain Shapes.

2022, March 9th - Computer Science Summit, UC Santa Barbara. Biomedical Shape Analysis with Geometric Learning.

2022, February 17th - Invited Lecture, University of British Columbia, Canada. Deep Generative Models for Molecular Reconstructions in Cryo-Electron Microscopy.

2022, January 26th - Materials Research Outreach Symposium, UC Santa Barbara. Shape Learning: From Images to Scientific Insights.

2022, January 25th - Physics Department Colloquium, UC Santa Barbara. Riemannian Geometry: From General Relativity to Biomedical Imaging.