2023, December 8th. Workshop Spatial Data Science in an Age of Scientific Disruption. Keynote: Geometric Artificial Intelligence.

2023, November 30th. Harvard University, Department of Applied Mathematics. The Differential Geometry of Neural Manifolds.

2023, November 28th. University of North Carolina at Chapel Hill, Applied Physical Sciences Colloquium. Architectures of Topological Deep Learning: A Survey of Topological Neural Networks.

2023, November 16th. UC Noyce Initiative's Launch of the Ann Bower's Women Brain Health Initiative. Artificial Intelligence for Brain Image Analysis: What Do We Know About the Female Brain? 

2023, October 6th. Workshop on Multiphysics Measurements and Bayesian Methods. A Survey of Topological Neural Networks. 

2023, August 17th. MIT Summer School of Geometry. Architectures of Topological Deep Learning: A Survey of Topological Neural Networks.

2023, July 18th - Eresfjord School in Mathematical Methods in Neuroscience. Geometry and Topology of Neural Manifolds.

2023, June 19th - University of British Columbia. Center for Brain Health. Architectures of Topological Deep Learning: A Survey of Topological Neural Networks.

2023, June 18th - CVPR Workshop on Computational Cameras and Displays. Deep Generative Modeling for Volume Reconstruction in Cryogenic Electron Microscopy: A Survey.

2023, June 18th - CVPR Workshop on Topology, Algebra and Geometry. (Keynote). Architectures of Topological Deep Learning: A Survey of Topological Neural Networks.

2023, June 8th - Flatiron Institute, Simons Foundation. CryoEM Summer Workshop. Deep Generative Modeling for Volume Reconstruction in Cryo-Electron Microscopy.

2023, May 31st - UCLA Applied Mathematics Seminar - Coding Differential Geometry for Machine Learning.

2023, May 15th - Ann S. Bowers Women’s Brain Health Initiative. Internal Kickoff. Geometric Deep Learning for Neurodegeneration.

2023, April 19th - IEEE Central Coast Event Talk - Geometric Learning for Shape Analysis from Bioimaging Data.

2023, April 17th - UCSB ECE Summit. Advancing Biomedicine with AI for Shape Analysis.

2023, April 15th - UCSB WISE Panels. Women in Science \& Engineering: Academic Careers.

2023, February 17th - UCSB Differential Geometry Seminar. Geomstats: coding differential geometry for machine learning.

2023, February 17th - UCSB Physics Graduate Seminar. Riemannian Geometry: From General Relativity to Biomedical Imaging.

2023, January 31st - Data Science Initiative @ SISSA - Bioshape Analysis with Geometric Learning.

2023, January 13th - UCSB Machine Learning Seminar. Geometric Machine Learning.