2026, May 18th. UCSB AI Library. AI-Powered Science and the Digital Twin Revolution. (Outreach).

2026, March 31st. UCSB Physics Colloquium. Symmetry in Brains and Machines.

2026, February 19th. UCSB REAL AI for Science Initiative. AI-Powered Science and the Digital Twin Revolution. (Outreach).

2026, January 9th. UCSB Spatial Navigation. The Geometry and Algebra of Spatial Navigation.

2025, June 18th. UCSB Center for Aging and Longevity. Direct Relief, Santa Barbara. Healthy and Pathological Aging: Unlocking the Brain with AI. (Outreach).

2024, February 9th. UCSB Physics Graduate Seminar. From Theoretical Physics to Geometric Intelligence.

2023, December 8th. UCSB Workshop Spatial Data Science in an Age of Scientific Disruption. Geometric Artificial Intelligence. (Outreach).

2023, April 17th. UCSB ECE Summit. Advancing Biomedicine with AI for Shape Analysis.

2023, April 15th. UCSB WISE Panels. Women in Science \& Engineering: Academic Careers (Outreach).

2023, February 17th. UCSB Differential Geometry Seminar. Geomstats: Coding Differential Geometry for Machine Learning.

2023, February 17th. UCSB Physics Graduate Seminar. Riemannian Geometry: From General Relativity to Biomedical Imaging.

2023, January 13th. UCSB Machine Learning Seminar. Geometric Machine Learning.

2022, November 16th. UCSB ECE Graduate Seminar. Geometric Machine Learning.

2022, April 13th. UCSB Cryo-EM FIB Forum. Deep Generative Models for Molecular Reconstructions in Cryo-Electron Microscopy.

2022, March 11th. UCSB Psych \& Brain Sciences Seminar. Brain Shapes.

2022, March 9th. UCSB CS Summit. Biomedical Shape Analysis with Geometric Learning.

2022, January 26th. UCSB Materials Research Outreach Symposium. Shape Learning: From Images to Scientific Insights. (Outreach).

2022, January 25th. UCSB Physics Colloquium. Riemannian Geometry: From General Relativity to Biomedical Imaging.

