2021, December 14th - Mathematical Engineering Seminar, UC Louvain. Riemannian Geometry in Statistics and Machine Learning.

2021, December 13th - Séminaire MINES Paristech - PSL Research University. Geomstats: a Package for Riemannian Geometry in Statistics and Machine Learning.

2021, November 19th - Physics Graduate Students Seminar, UC Santa Barbara. From General Relativity to Biomedical Imaging.

2021, November 5th - Toronto Geometry Colloquium. Exploring the Geometries of Life. (Video). 

2021, October 27th - Banff International Research Station's workshop BIRS-CMO Geometry \& Learning from Data. Geomstats: a Python package for Geometry \& Learning from Data (Video).

2021, October 13th - Probability Seminar, UC Santa Barbara. Geometric Statistics for Biological Shape Analysis.

2021, July 14th - 63rd ISI World Statistics Congress 2021. Submanifold learning with Riemannian Variational Autoencoders.

2021, July - Stanford University. Invited Lecture. Probability distributions on manifolds.

2021, February 17th - UC Davis, Seminar on Inference for Dynamical Systems. Geomstats: a Python package for Riemannian geometry in dynamical systems.

2020, March 30th - Lausanne, Switzerland. Workshop on Statistics for Indirectly Measured Functional Data. 3D shape reconstruction with pose estimation: what is the right metric?

2020, March 23th - Oberwolfach, Germany. Workshop on Optimization on Riemannian manifolds. Geomstats: a Python package for Riemannian geometry in machine learning.

2020, November 15th - Math Bio Seminar of the University of British Columbia. Geometric Statistics for shape analysis of bioimaging data.

2020, October  1st - Stanford University, USA. Probability distributions on a Riemannian manifold.

2020, March 10th - Harvard Medical School, USA. Advancing cancer research with analysis of bioimaging data.

2020, February 19th - UC Santa Barbara, USA. Seminar of Electrical and Computer Engineering. Advancing medical research with shape analysis of bioimaging data.

2020, February 13th - Stanford SLAC, USA. Seminar of Artificial Intelligence. Shape learning.

2020, January 23th - Georgia Tech, USA. Seminar of Mathematics \& Biology. Shape analysis of bioimaging data.

2020, January 8th - UC Davis, USA. Statistics Seminar. Statistical shape analysis for bioimaging data.

2019, September 5th -  Toulouse, France. Workshop on Geometric Statistics. Learning weighted submanifolds using geometric variational autoencoders.

 2019, August 29th -  Toulouse, France. Geometric Science of Information Conference. Geomstats: a Python package for Riemannian geometry in machine learning.

2019, June 18th - Salt Lake City, USA. Math in the Desert Workshop. Submanifold learning with variational autoencoders: Application to brain manifold learning.

2019, March 16th - San Francisco, USA. Molecular Med Tri-Conference \& Bio-IT West. Building a Computational Model of the Human Anatomy using Medical Images.

2019, February 20th - Berkeley, USA. Seminar of UC Berkeley. Statistics on Shape Data: Correcting an Asymptotic Bias in Template Shape Estimation.

2018, July 15th - Stockholm, Sweden. International Conference of Machine Learning (ICML), Workshop Geometry in Machine Learning (GiMLi). Geometric Statistics: Learning from Medical Images?

2018, May 19th - Baltimore, USA. Seminar of John Hopkins University, Center of Imaging Science. Geometric Statistics for Image Analysis.

2018, January 28th - Oberwolfach, Germany. Meeting of the Mathematisches Forschungsinstitut Oberwolfach.Geometric Statistics for Computational Anatomy in the Session on Statistics for Data with Geometric Structures.

2017, December 16th - London, UK. 10th International Conference on Computational and Methodological Statistics (CMStatistics 2017). Geometric Statistics for Computational Anatomy in the Session on Statistics for data with geometric structure.

2017, November 16th - Cambridge, UK. Shape analysis and computational anatomy workshop. Template shape estimation: correcting an asymptotic bias.

2017, December 20th - Goettingen, Germany. Goettingen Statistics Seminar. Open questions in Geometric Statistics.

2017, December 13th - London, UK. BioMedIA Seminar of the Department of Computing, Imperial College London.Geometric Statistics for medical image computing.

2017, November 29th - Kingston, Canada. Seminar at Queen's Hospital. AI for Diagnostic Radiology.

2017, September 23rd - Orlando, USA. American Mathematical Society (AMS) Sectional Meeting. Estimation on manifolds: synchronization of rotations for cryo-electron microscopy in the Special Session on Mathematics of Biomolecules: Discrete, Algebraic, and Topological.

2016, June 7th - Stanford, USA. Stanford Statistics Seminar. Template shape estimation in Computational Anatomy. 

2015, November 2nd - Montpellier, France. Statistics Seminar of Université de Montpellier. Statistical properties of the Fréchet mean in quotient spaces. Applications to Computational Anatomy. 

2015, February 19th - Vienna, Austria. International Workshop on Infinite-Dimensional Riemannian Geometry with Applications to Image Matching and Shape Analysis. Erwin Schroedinger International Institute for Mathematics and Physics. Noise Effects on Quotient Spaces M/G. 