2026, April 20th. Long Now Foundation, San Francisco. The Geometry of Consciousness.

2026, April 14th. International Winter Neuroscience Conference. Symmetry in Brains and Machines.

2026, February 26th. University of Texas, Dallas' School of Behavioral and Brain Sciences, Center for Brain Health. Digital Twin Brain to Catapult Precision Brain Health.

2025, October 23rd. McMaster University Seminar. Topological Deep Learning.

2025, October 9th. Montecito Ideas Club. Healthy and Pathological Aging: Unlocking the Brain with AI. (Outreach).

2025, July 9th. Cold Spring Harbor Laboratory Seminar Series. Geometric Intelligence in Minds and Machines.

2025, June 3rd. Stanford University, Workshop Bridging Biology and Statistics In Honor of Professor Holmes. The Role of AI in Advancing Women's Brain Health.

2025, April 30th. NSF-Simons National Institute for Mathematics and Theory in Biology (NITMB), Workshop New Developments in the Theory and Methodology of Graph Neural Networks. Topological Deep Learning.

2025, April 2nd. Instituto de Matemáticas, Geometric Intelligence Workshop. Geometric Intelligence in Minds and Machines.

2025, March 31st. COSYNE Workshop on GNNs and Graphical Analysis in Neuroscience. A Survey of Message Passing Topological Neural Networks.

2025, February 26th. University of Texas, Dallas' School of Behavioral and Brain Sciences, Center for Brain Health. AI and the Digital Twin Brain.

2025, February 21st. NeurReps Seminar Series. Geometric Intelligence in Minds and Machines.

2025, February 18th. Chan-Zuckerberg Initiative Seminar. Leveraging AI for Women’s Brain Health Research.

2025, February 10th. Erwin Schrödinger International Institute. G-Invariance in G-Equivariant Networks.

2024, October 15th. Noyce Foundation Annual Event. The Role of AI in Advancing Women’s Brain Health.

2024, August 8th. Cognitive Computational Neuroscience Conference, Battle of the Metrics Community Event. Riemannian Geometry of Neural Representations in Natural and Artificial Intelligence.

2024, July 27th. ICML Workshop on Geometry-grounded Representation Learning and Generative Modeling. Geometric Intelligence.

2024, July 15th. Eresfjord School in Mathematical Methods in Computational Neuroscience. Hierarchical Equivariance in Artificial and Natural Brains.

2024, June 17th. MIT DHIVE Program. Digital Twins and the Role of AI in Advancing Women’s Brain Health.

2024, May 28th. UC Riverside Seminar. Robust G-Invariance in G-Equivariant Networks.

2024, May 13th. Bowers Women’s Brain Health Seminar. Digital Twins and the Role of AI in Advancing Women’s Brain Health.

2024, February 13th. Caltech’s Math \& Machine Learning Seminar. Robust G-Invariance in G-Equivariant Networks.

2024, January 25th. University of Chicago, Institute for Mathematical and Statistical Innovation, Workshop on Graph Neural Networks for the Sciences. A Survey of Message Passing Topological Neural Networks.

2023, November 30th. Harvard University, Department of Applied Mathematics. The Differential Geometry of Neural Manifolds.

2023, November 28th. University of North Carolina at Chapel Hill, Applied Physical Sciences Colloquium. Architectures of Topological Deep Learning: A Survey of Topological Neural Networks.

2023, August 17th. MIT Summer School of Geometry. Architectures of Topological Deep Learning: A Survey of Topological Neural Networks.

2023, July 18th. Eresfjord School in Mathematical Methods in Computational Neuroscience. Geometry and Topology of Neural Manifolds.

2023, June 19th. University of British Columbia, Center for Brain Health. Architectures of Topological Deep Learning: A Survey of Topological Neural Networks.

2023, June 18th. CVPR Workshop on Computational Cameras and Displays. Deep Generative Modeling for Volume Reconstruction in Cryo-Electron Microscopy: A Survey.

2023, June 8th. Flatiron Institute, Simons Foundation, CryoEM Summer Workshop. Deep Generative Modeling for Volume Reconstruction in Cryo-Electron Microscopy.

2023, May 31st. UCLA Applied Mathematics Seminar. Coding Differential Geometry for Machine Learning.

2023, April 19th. IEEE Central Coast Event Talk. Geometric Learning for Shape Analysis from Bioimaging Data.

2023, January 31st. Data Science Initiative at SISSA. Bioshape Analysis with Geometric Learning.

2022, October 11th. INRIA Saclay, Seminar of the SODA and MIND (previously Parietal) teams. Geomstats: A Python Package for Geometry in Machine Learning.

2022, October 10th. Institut Poincaré, Workshop on Geometry, Topology in Statistics and Data Science. Geomstats: A Python Package for Geometry in Machine Learning.

2022, September 29th. SIAM Conference on Mathematics of Data Science, Mini Symposium of Statistics and Machine Learning in Topological and Geometric Data Analysis. Geomstats: A Python Package for Differential Geometry in Machine Learning.

2022, September 7th. Geo2Int (Geometry and Geometric Integration) Workshop. Geomstats: A Python Package for Differential Geometry in Machine Learning.

2022, June 8th. University of Washington, eScience Institute Seminar. Geometric Learning for Shape Analysis in Bioimaging.

2022, June 1st. Sage Math Conference. Geomstats: A Python Package for Differential Geometry in Machine Learning.

2022, May 6th. Pacific Institute for the Mathematical Sciences (PIMS) Workshop. CompSPI: Open-Source Software for Biological Imaging.

2022, May 2nd. Johns Hopkins University, Center for Imaging Science Workshop. Geometric Learning for Shape Analysis from Bioimaging. 